Discordance LV - TF

### 2023-06-07 reporting/discordance LV TF.Rmd
update results

---
title: "Discordance LV - TF"
author: "TF"
date: "`r Sys.Date()`"
output: html_document
---

@@

```{r eval=TRUE, fig.cap="Original plot", fig.height=20, include = TRUE, out.height=700, out.width=700}
knitr::include_graphics("../images/comparison_methods6-1.pdf")
```

```{r eval=TRUE, fig.cap="New plot (fails to replicate)", fig.height=20, include = TRUE, out.height=700, out.width=700}
knitr::include_graphics("../images/plot_original.pdf")
```

@@

```{r}
tau <- 0.5

@@

-   Nothing corresponds to case == 'A' in LV script
-   There is no scenario in the paper where beta follows gaussian distribution with mean -0.5 (beta == 1 in LV script)
-   The variance defined in LV when beta != 1 corresponds to type == "C" in TF (because tau = 0.5)

It makes sense regarding the graph because results from type == "C" are mostly similar. Problem identified !!

>>>>

---
title: "Discordance LV - TF"
author: "TF"
date: "`r Sys.Date()`"
output:
  bookdown::github_document2:
    toc: TRUE
---

@@

# Plots

## Draft plot

```{r eval=TRUE, fig.cap="Original plot", fig.height=20, include = TRUE, out.height=700, out.width=700, echo=FALSE}
knitr::include_graphics("images/comparison_methods6-1.png")
```

# New plot (fails to replicate)

```{r eval=TRUE, fig.cap="New plot (fails to replicate)", fig.height=20, include = TRUE, out.height=700, out.width=700, echo=FALSE}
knitr::include_graphics("images/plot_original.png")
```

@@

```{r}
if (params[ite,1]==0.1){
  gsp=0.3
}
if (params[ite,1]==0.3){
  gsp=0.4
}

if (params[ite,1]==0.5){
  gsp=0.5
}
gsize<-50 #gene set size
#gsp<-agsp[sigp]
ngs<-gsize*gsp
tau <- 0.5

@@

-   Nothing corresponds to case == 'A' in LV script
-   There is no scenario in the paper where beta follows gaussian distribution with mean -0.5 (beta == 1 in LV script)
-   The variance defined in LV when beta != 1 corresponds to type == "C" in TF (because tau = 0.5)
- The proportion of significant gene does not match the ones in the paper
